### 2021-05-20 doc/thesis/chapters/dsp.tex
new headlines
update

On the receiver side, once the signal reaches the antenna of a receiver, there are further similarities.
The antenna signal needs to be amplified and filtered.
Both steps depend on the antenna characteristics, but usually the received signal is of relatively low power, and the antenna receives a wider range of frequencies than required.
The filter therefor selects the frequency area that is of interest.
Another reason for the filter is to avoid spectral replicas in the subsequent modulation, or down-conversion.
Here, the front-end often down-converts to a low intermediate frequency, instead of directly going to baseband.
The intermediate frequency is then modulated, or mixed, down to baseband later in the digital domain, which brings advantages in the downstream processing chain. %TODO check this or explain more which advantages (HF to BB directly --> i/q complex signal? ; HF to IF to BB --> real signal ) ??

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Antenna signal to }

block diagram of superheterodyne

>>>>

On the receiver side, once the signal reaches the antenna of a receiver, there are further similarities.
The antenna signal needs to be amplified and filtered at first.
Both steps depend on the antenna characteristics, but usually the received signal is of relatively low power, and the antenna receives a wider range of frequencies than required.
The filter therefor selects the frequency area that is of interest.
Another reason for the filter is to avoid spectral replicas in the subsequent modulation, or down-conversion.
Here, the front-end often down-converts to a low intermediate frequency, instead of directly going to baseband.
The intermediate frequency is then shifted down to baseband by a modulator later in the digital domain, which brings advantages in the downstream processing chain. %TODO check this or explain more which advantages (HF to BB directly --> i/q complex signal? ; HF to IF to BB --> real signal ) ??

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Receiver types}

\subsection{heterodyne}
block diagram

\subsection{super-heterodyne}
block diagram

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Down-Conversion}

from HF to BB\\
math. formulas
